\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Assessing income inequality with tax data - Switzerland from 1917 to 2010}

### 2014-12-16 paper/subdocuments/results.Rnw
modified visual parameters for figure1234

<<with_without_zeros_Gini,warning=FALSE, fig.cap='Gini coefficients with, without and imputed non-taxed units',fig.pos='H'>>=
df <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
#library(reshape)
dflong <- melt(df[,c("G_steink","G_steink0","G_steink_halb","kanton","bemessungsjahre")], id=c("kanton","bemessungsjahre"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("without non-taxed","including non-taxed","imputed values for non-taxed")
fig_zeros <- ggplot(dflong[dflong$kanton=="CH"&dflong$bemessungsjahre>=2003,], 
       aes(x=bemessungsjahre,y=Gini,shape=Type,linetype=Type))+
  scale_y_continuous(limits=c(0.28,0.55))+
  scale_x_continuous(limits=c(1970,2011),breaks=number_ticks(10)) +
  geom_line(size=0.5)+
  geom_point(aes(shape=Type),size=3)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Influence of non-taxed")
fig_zeros

@@

estv_masse_long$measure <- factor(estv_masse_long$variable)
estv_masse_long$Year <- as.double(as.character(estv_masse_long$Year))
estv_masse_long <- estv_masse_long %>% group_by(measure) %>% mutate(log_value=log(value)-log(value)[1])
fig_measures <- ggplot(estv_masse_long, aes(x=Year,y=log_value,shape=measure))+
  #scale_y_continuous(limits=c(0,0.55))+
  scale_x_continuous(limits=c(1945,2011),breaks=number_ticks(10)) +
  geom_point(aes(shape=measure),size=3)+
  geom_line(aes(linetype=measure))+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Using different inequality measures")
fig_measures

>>>>

<<with_without_zeros_Gini,warning=FALSE, fig.cap='Gini coefficients with, without and imputed non-taxed units',fig.pos='H'>>=
df <- read.csv("../../data/ginis_und_perzentile_normal.csv",sep="\t")
#library(reshape)
dflong <- melt(df[,c("G_steink","G_steink0","G_steink_halb","kanton","bemessungsjahre")], id=c("kanton","bemessungsjahre"))
names(dflong)[3]<-"Type"
names(dflong)[4]<-"Gini"
levels(dflong$Type)<-c("without non-taxed","including non-taxed","imputed values for non-taxed")
dflong$Gini[dflong$kanton=="CH"&dflong$bemessungsjahre<2003&dflong$Type=="including non-taxed"]<-NA
dflong$Gini[dflong$kanton=="CH"&dflong$bemessungsjahre<2003&dflong$Type=="imputed values for non-taxed"]<-NA
fig_zeros <- ggplot(dflong[dflong$kanton=="CH",], 
       aes(x=bemessungsjahre,y=Gini,shape=Type,linetype=Type))+
  scale_y_continuous(limits=c(0.28,0.55))+
  scale_x_continuous(limits=c(1970,2011),breaks=number_ticks(10)) +
  geom_line(size=0.5)+
  geom_point(aes(shape=Type),size=3)+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Influence of non-taxed")
fig_zeros

@@

estv_masse_long$measure <- factor(estv_masse_long$variable)
estv_masse_long$Year <- as.double(as.character(estv_masse_long$Year))
estv_masse_long <- estv_masse_long %>% group_by(measure) %>% mutate(log_value=log(value)-log(value)[1])
fig_measures <- ggplot(estv_masse_long, aes(x=Year,y=log_value,shape=measure))+
  scale_y_continuous(limits=c(-0.7,0.45))+
  scale_x_continuous(limits=c(1945,2011),breaks=number_ticks(10)) +
  geom_point(aes(shape=measure),size=3)+
  geom_line(aes(linetype=measure))+
  theme_bw()+
  xlab("Year")+
  theme(legend.justification=c(0,1),legend.position=c(0, 1))+
  ggtitle("Using different inequality measures")
fig_measures
